A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-10-16 alpibot.tex
Versión casi lista, integrada con los cambios de Luciano.  Solo falta la aclaración de Juan.

\noindent where $pulses_{l}$ and $pulses_{r}$ are the pulses obtained for the left and right encoder.  Pulses refer to natural discrete numbers that represents the circular movement of the encoder shaft.  The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder. These equations provide the estimated values for the left $l_L$ and right $l_R$  thread longitude.   The initial position of the threads is configurable.

@@

\begin{figure*}[!t]
\centering
\subfloat[Case I]{\includegraphics[width=15cm]{images/alpibot2.jpg}\label{subject8}}
\caption{Top view of the robot prototype.  The SBC is shown on the center, alongside the Arduino Mega board.  Both reels can be seen on the same vertical plane of the wheel axis. A power bank (white) is located on one side of the robot, and on the rear part, the motor power battery (black) is located.}
\label{fig:alpibot2}
\end{figure*}

@@

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration whose units are expressed in $[\frac{1}{s}]$, and $l_D$ is a constant offset in $[m]$ that is used to customize the desired length of the thread where the robot does not move.   As shown on Figure~\ref{fig:follow_params},  $l_L$ and $l_R$ are changes in thread longitudes (the length of thread that was released from each reel) in $[m]$  obtained from encoder information from Equation~\ref{eq:encoder_len}, $V_t$ is the estimated forward velocity for the target and finally $\omega_{L}$ are $\omega_{R}$ are the velocity values that are directly used to drive each wheel motor.

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_{off}$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_{off}$ is similar to $l_D$, and is used to customize the length of the thread where the robot does not move at all. Lastly, $base_{vr}$, is another constant used to determine the minimum rotational velocity of the vehicle.

\begin{algorithm}[]
\caption{Rotate and go algorithm}
\begin{algorithmic}
\STATE $Dt \gets l_L - l_R$
\STATE $Dm \gets \frac{l_R+l_L}{2}$
\STATE $V_r \gets c_r * (abs(Dt) - Dt_{off}) + base_{vr}$ 
\STATE $V_f \gets c_v * (Dm - Dm_{off})$

@@

We performed an additional simulated experiment to validate whether or not the selected algorithm could be extended to handle weight of the real oxygen tank. A common type of tank used in this type of therapies is a 5kg oxygen tank.

>>>>

\noindent where $pulses_{l}$ and $pulses_{r}$ are the pulses obtained for the left and right encoder.  Pulses refer to natural discrete numbers that represents the circular movement of the encoder shaft.  The variable $r$ is the radius of the reel and $ppr$ is the pulses per revolution (resolution) of the encoder. These equations provide the estimated values for the left $l_L$ and right $l_R$, which are the length of thread released from each reel.   The initial position of the threads is configurable.

@@

\begin{figure*}[!t]
\centering
\subfloat{\includegraphics[width=15cm]{images/alpibot2.jpg}\label{subject8}}
\caption{Top view of the robot prototype.  The SBC is shown on the center, alongside the Arduino Mega board.  Both reels can be seen on the same vertical plane of the wheel axis. A power bank (white) is located on one side of the robot, and on the rear part, the motor power battery (black) is located.}
\label{fig:alpibot2}
\end{figure*}

@@

\noindent where  $c_v$ and $c_{\alpha}$ are constant coefficients used for calibration whose units are expressed in $[\frac{1}{s}]$, and $l_D$ is a constant offset in $[m]$ that is used to customize the desired length of the thread where the robot does not move.   As shown on Figure~\ref{fig:follow_params},  $l_L$ and $l_R$ are changes in the length of thread that was released from each reel in $[m]$  obtained from encoder information from Equation~\ref{eq:encoder_len}, $V_t$ is the estimated forward velocity for the target and finally $\omega_{L}$ are $\omega_{R}$ are the velocity values that are directly used to drive each wheel motor.

@@

The procedure is detailed in Algorithm~\ref{alg:rotateandgoalg}.  The variable $V_r$ is the speed at which the vehicle will rotate on its axis, and $V_f$ is the speed at which the vehicle will move forward once it can move on the subject's direction.  The algorithm requires three parameters, $c_v$ and $c_r$ that regulates the coefficients for the forward and rotation movement, and an additional parameter $Dt_{off}$ that regulates the sensibility of the rotation movement.  The constant parameter $Dm_{off}$ is similar to $l_D$, and is used to customize the length of the thread where the robot does not move at all. Temporary variables $Dt$ and $Dm$ are used in the algorithm to calculate the difference and the average of the changes in released thread. Lastly, $base_{vr}$, is another constant used to determine the minimum rotational velocity of the vehicle.

\begin{algorithm}[]
\caption{Rotate and go algorithm}
\begin{algorithmic}
\STATE \textbf{Define} $Dt \gets l_L - l_R$
\STATE \textbf{Define} $Dm \gets \frac{l_R+l_L}{2}$
\STATE $V_r \gets c_r * (abs(Dt) - Dt_{off}) + base_{vr}$ 
\STATE $V_f \gets c_v * (Dm - Dm_{off})$

@@

We performed an additional simulated experiment to validate whether or not the selected algorithm could be extended to handle weight of the real oxygen tank. A common type of tank used in this type of therapies is a 5 kg oxygen tank.
